Estimate of the Neural Net Dimension Using Algebraic Topology and Lie Theory\thanks{The code can be found at: \href{https://github.com/karhunenloeve/Irhe}{https://github.com/karhunenloeve/Irhe}.}

### 2020-06-17 llncs2e/figure1.tex
update paper

\begin{figure}[t!]
\begin{tikzpicture}[
	bullet/.style={circle,
	fill,
	inner sep=2pt,
	label={#1}},
	>=latex,
	scale=0.5
]
	\draw[color=gray] (0,0) circle (85pt);
	\node[above, color=gray] at (2.5,2) {$\mathcal{S}^1$};
	\node[above] at (-5,-3) {(a)};
	\draw [black,line width=0.5pt,/.list={1/6,1/2,5/6}]
	(210:3) node[color = brick, bullet={below left:1}] (a) {}
	-- (90:3) node[color = brick, bullet={above:2}] (b) {}
	-- (-30:3) node[color = brick, bullet={below right:3}] (c) {}
	-- cycle;
	\node[above] at (-5,2) {$K_0 = \{\{1\}, \{2\}, \{3\}\}$};
	\node[above, fill=white] at (-4,1) {$K_1 = \{\{1,2\}, \{1,3\}, \{2,3\}\}$};
	\node[above, fill=white] at (-5,0) {Coefficients in $\mathbb{Z}/2\mathbb{Z}$};
\end{tikzpicture}
\begin{tikzpicture}[
	bullet/.style={circle,
	fill,
	inner sep=2pt,
	label={#1}},
	>=latex,
	scale=0.5
]
	\node[above, color=gray] at (2.5,2) {$\mathcal{S}^1$};
	\draw[color=gray] (0,0) circle (85pt);
	\node[above] at (-5,-3) {(b)};
	\draw [black,line width=0.5pt,->-/.list={1/6,1/2,5/6}]
	(210:3) node[color = brick, bullet={below left:1}] (a) {}
	-- (90:3) node[color = brick, bullet={above:2}] (b) {}
	-- (-30:3) node[color = brick, bullet={below right:3}] (c) {}
	-- cycle;
	\draw[line width=0.5pt,-{Latex[bend]}] (240:0.5) arc(240:-60:0.5);
	\node[above] at (-5,2) {$K_0 = \{\{1\}, \{2\}, \{3\}\}$};
	\node[above, fill=white] at (-3.9,1) {$K_1 = \{\{1,2\}, \{2,3\}\}, \{1,3\}\}$};
	\node[above] at (-5.7,0) {Coefficients in $\mathbb{R}$};
\end{tikzpicture}
\caption{Two triangulations of $\mathcal{S}^1$. We compute $H_0(\mathcal{S}^1) = \ker(\partial_0) / \Ima(\partial_1)$ for (a) and (b), see Sect. \ref{simcomplexhomtheory}. For (a): $\ker(\partial_0) = \text{span}(\{1\},\{2\},\{3\})$ and $\Ima(\partial_1)= \text{span}(\{\{2\}-\{1\}\},\{\{3\}-\{2\}\})$ as linearly independent elements. Observe that $\{1\}-\{3\}=\{2\}-\{1\}-(\{3\}-\{2\})$ holds. Thus $\ker(\partial_0) \simeq (\mathbb{Z}/2\mathbb{Z})^3$, $\Ima(\partial_1)=(\mathbb{Z}/2\mathbb{Z})^2$ and $H_0(\mathcal{S}^1;\mathbb{Z}/2\mathbb{Z}) = \mathbb{Z}/2\mathbb{Z}$. For (b): $\ker(\partial_0) = \text{span}(\{1\},\{2\},\{3\})$, but due to real coefficients the linear dependency is this time given by $\{2-1\} = \{3-2\}$. Thus $\ker(\partial_0) \simeq \mathbb{R}^3$ and $\Ima(\partial_1)=\mathbb{R}^2$, which yields the homology group $H_0(\mathcal{S}^1;\mathbb{R}) = \mathbb{R}$.}
\label{complexes}
\end{figure}

>>>>

\begin{figure}[t]
    \begin{overpic}[width=\textwidth,tics=10]{figure1.pdf}
        \put (0.9,58) {\textbf{a})}
        \put (0.9,28) {\textbf{b})}
        \put (70,58) {\textbf{c})}
        \put (8.8,29.6) {$0$}
        \put (32.8,29.6) {$0$}
        \put (58,29.6) {$0$}
        \put (74.8,43.6) {\small{1}}
        \put (90.5,43.6) {\small{2}}
        \put (84.6,22.4) {\small{3}}
        \put (84.6,1) {\small{4}}
        \put (7,13) {$K_1$}
        \put (31,13) {$K_2$}
        \put (57,13) {$K_3$}
        \put (21,13) {$\subseteq$}
        \put (45,13) {$\subseteq$}
        \put (32,39) {$B_k$}
        \put (32,49) {$Z_k$}
        \put (32,55) {$C_k$}
        \put (56,39) {$B_{k-1}$}
        \put (56,49) {$Z_{k-1}$}
        \put (56,55) {$C_{k-1}$}
        \put (7,39) {$B_{k+1}$}
        \put (7,49) {$Z_{k+1}$}
        \put (7,55) {$C_{k+1}$}
        \put (19.5,56) {$\partial_{k+1}$}
        \put (44.5,56) {$\partial_{k}$}
        \put (92,37) {{\color{red5} $\bullet$} $H_0$}
        \put (92,34) {{\color{red4} $\bullet$} $H_1$}
        \put (92,31) {{\color{red3} $\bullet$} $H_2$}
        \put (92,28) {{\color{red2} $\bullet$} $H_3$}
        \put (92,25) {$\cdots$}
        \put (92,15.5) {{\color{red5} $\bullet$} $H_0$}
        \put (92,12.5) {{\color{red4} $\bullet$} $H_1$}
        \put (92,9.5) {{\color{red3} $\bullet$} $H_2$}
        \put (92,6.5) {{\color{red2} $\bullet$} $H_3$}
        \put (92,3.5) {$\cdots$}
    \end{overpic}\\[0.1cm]
    \caption{\textbf{a}) Illustration of the chain complex following Zomorodian et al. \cite{ZomorodianC05}. \textbf{b}) Sublevel sets of a simplicial complex connected by inclusion. \textbf{c}) Pipeline for persistent homology: \textbf{c})1. Loading point sets. \textbf{c})2. Computation of a filtration. \textbf{c})3. Computation of persistent homology with confidence band. \textbf{c})4. Computation of persistence landscapes.}
    \label{figure1}
\end{figure}

### 2020-06-17 llncs2e/figure2.tex
update paper

\begin{figure}[t!]
\centering
\begin{tikzcd}
& M\simeq \mathbb{R}^n \arrow[ld, "x^{(0)}", bend right = 15] 
& U \simeq \mathbb{R}^{n-k} \arrow[ld, "x^{(1)}" pos=0.8, swap, bend right = 15] \arrow[d, "x^{(2)}"] \arrow[rd, "x^{(L-1)}", bend left = 15] \arrow[l, hook', swap, "\imath"] 
&\\
x^{(0)}(M) \arrow[r, "\varphi^{(0)}"] 
& x^{(1)}(U) \arrow[r, leftrightarrow, "\varphi^{(1)}"]
& x^{(2)}(U) \arrow[r, leftrightarrow, "\varphi^{(L-1)}", dotted]
& x^{(L-1)}(U) \arrow[r, hook, "\varphi^{(L)}"]
& x^{(L)}(M)
\end{tikzcd}
\caption{The architecture of the neural net maps over $\varphi^{(0)}$ into a subspace of $M$, in
which the searched manifold $U$ of the data can be embedded. The maps $\varphi^{(1)}, \cdots, \varphi^{(L-1)}$
are models of bijective, smooth and therefore diffeomorphic functions.}
\label{architecture}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\begin{tikzpicture}
\begin{axis}[
	height=2.2in,
	width= 2.6in,
	axis x line = bottom,
	axis y line = left,
	minor x tick num=10,
	ylabel={$\frac{\epsilon_i + \epsilon_{j+1}}{2}$},
	xlabel={\textbf{a}) Persistence landscape \texttt{cifar10}.},
	xmin=0,
	xmax=1050,
	ymin=0,
	ymax=650,
	ticklabel style={font=\small},
	x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
	y label style={at={(axis description cs:0.20,0.85)},rotate=-90,anchor=south, fill=white},
	axis line style={-{Latex[length=1.5mm,width=1.5mm]}}
]
\coordinate (spypoint) at (axis cs:88,50);
\coordinate (magnifyglass) at (axis cs:800,400);
\draw [thick, dotted, draw=gray] (axis cs: 0,580) -- (axis cs: 1050,580) node[pos=0.9, below] {$\infty$};
\end{axis}
\begin{scope}[spy using outlines={circle, magnification=4, connect spies}]
\node[inner sep=0pt] at (2.38,1.77) {\includegraphics[width=0.39\textwidth]{figure2_a.pdf}};
\spy [lightgray, size=2cm] on (spypoint) in node[fill=white] at (magnifyglass);
\end{scope} 
\end{tikzpicture}
\begin{tikzpicture}
\begin{axis}[
	height=2.2in,
	width= 2.6in,
	axis x line = bottom,
	axis y line = left,
	minor x tick num=10,
	xlabel={\textbf{b}) Persistence landscape \texttt{cifar100}.},
	xmin=0,
	xmax=1050,
	ylabel={$\cdot 10^{3}$},
	ymin=0,
	ymax=5,
	ticklabel style={font=\small, fill=white},
	x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
	y label style={at={(axis description cs:0.1,0.9)},rotate=-90,anchor=south},
	axis line style={-{Latex[length=1.5mm,width=1.5mm]}}
]
\draw [thick, dotted, draw=gray] (axis cs: 0,4.45) -- (axis cs: 1050,4.45) node[pos=0.9, below] {$\infty$};
\end{axis}
\node[inner sep=0pt] (h) at (2.38,1.77) {\includegraphics[width=0.39\textwidth]{figure2_b.pdf}};
\node[inner sep=0pt] (h) at (4.5,2.7) {{\color{red5}$\bullet$} {$H_0$}};
\node[inner sep=0pt] (h) at (4.5,2.3) {{\color{red4}$\bullet$} {$H_1$}};
\node[inner sep=0pt] (h) at (4.5,1.9) {{\color{red3}$\bullet$} {$H_2$}};
\node[inner sep=0pt] (h) at (4.5,1.5) {{\color{red2}$\bullet$} {$H_3$}};
\node[inner sep=0pt] (h) at (4.5,1.1) {{\color{red1}$\bullet$} {$H_4$}};
\end{tikzpicture}
\begin{tikzpicture}
	\begin{axis}[
	table/col sep=comma,
	xlabel={\textbf{c}) Validation loss \texttt{cifar10}.},
	height=2.2in,
	width= 2.6in,
   	ticklabel style={font=\small, fill=white},
	xticklabel style={rotate=90, anchor=near xticklabel},
	x label style={at={(axis description cs:0.5,-0.15)},anchor=north},
	xtick={0,0.1,0.2,0.4,0.6,0.8,1},
    xticklabels={dummy,0,50,100,150,200,250},
	]
	\end{axis}
	\node[inner sep=0pt] at (2.51,2.08) {\includegraphics[width=0.343\textwidth, height=3.84cm]{figure2_c.pdf}};
\end{tikzpicture}
\begin{tikzpicture}
	\begin{axis}[
	table/col sep=comma,
	xlabel={\textbf{d}) Validation loss \texttt{cifar100}.},
	height=2.2in,
	width= 2.6in,
	ticklabel style={font=\small, fill=white},
	xticklabel style={rotate=90, anchor=near xticklabel},
	x label style={at={(axis description cs:0.5,-0.15)},anchor=north},
	xtick={0,0.1,0.2,0.4,0.6,0.8,1},
    xticklabels={dummy,0,50,100,150,200,250},
	]
	\end{axis}
	\node[inner sep=0pt] at (2.51,2.08) {\includegraphics[width=0.343\textwidth, height=3.84cm]{figure2_d.pdf}};
\end{tikzpicture}
\caption{a) Persistence landscape for \texttt{cifar10} and b) for the \texttt{cifar100} dataset \cite{krizhevsky2009learning}. Persistence landscapes are computed up to a resolution of $10^3$. c) and d) show the \texttt{MSE} loss function on the validation dataset using a $7:3$ split.}
\label{figure2}
\end{figure}

### 2020-06-17 llncs2e/figure3.tex
update paper

\begin{figure}[t!]
\begin{tikzpicture}
\begin{axis}[
	height=2.3in,
	width= 2.7in,
	axis x line = bottom,
	axis y line = left,
	minor x tick num=10,
	ylabel={$\frac{\omega_i + \omega_{j+1}}{2}$},
	xlabel={(a) cifar10.},
	xmin=0,
	xmax=1050,
	ymin=0,
	ymax=650,
	ticklabel style={font=\small},
	x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
	y label style={at={(axis description cs:0.20,0.85)},rotate=-90,anchor=south, fill=white},
	axis line style={-{Latex[length=1.5mm,width=1.5mm]}}
]
\coordinate (spypoint) at (axis cs:85,50);
\coordinate (magnifyglass) at (axis cs:800,400);
\draw [thick, dotted, draw=gray] (axis cs: 0,580) -- (axis cs: 1050,580) node[pos=0.9, below] {$\infty$};
\end{axis}
\begin{scope}[spy using outlines={circle, magnification=4, connect spies}]
\node[inner sep=0pt] at (2.55,1.9) {\includegraphics[width=0.42\textwidth]{figure3_a.pdf}};
\spy [lightgray, size=2cm] on (spypoint) in node[fill=white] at (magnifyglass);
\end{scope} 
\end{tikzpicture}\hfill
\begin{tikzpicture}
\begin{axis}[
	height=2.3in,
	width= 2.7in,
	axis x line = bottom,
	axis y line = left,
	minor x tick num=10,
	xlabel={(b) cifar100.},
	xmin=0,
	xmax=1050,
	ylabel={$\cdot 10^{3}$},
	ymin=0,
	ymax=5,
	ticklabel style={font=\small, fill=white},
	x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
	y label style={at={(axis description cs:0.1,0.9)},rotate=-90,anchor=south},
	axis line style={-{Latex[length=1.5mm,width=1.5mm]}}
]
\draw [thick, dotted, draw=gray] (axis cs: 0,4.45) -- (axis cs: 1050,4.45) node[pos=0.9, below] {$\infty$};
\end{axis}
\node[inner sep=0pt] (h) at (2.55,1.9) {\includegraphics[width=0.42\textwidth]{figure3_b.pdf}};
\node[inner sep=0pt] (h) at (4.5,3.1) {{\color{blacky}$\bullet$} {$H_0$}};
\node[inner sep=0pt] (h) at (4.5,2.7) {{\color{gray}$\bullet$} {$H_1$}};
\node[inner sep=0pt] (h) at (4.5,2.3) {{\color{purpur}$\bullet$} {$H_2$}};
\node[inner sep=0pt] (h) at (4.5,1.9) {{\color{brick}$\bullet$} {$H_3$}};
\node[inner sep=0pt] (h) at (4.5,1.5) {{\color{fire}$\bullet$} {$H_4$}};
\end{tikzpicture}
\caption{Mean confident persistence landscapes of the investigated datasets cifar10 and cifar100 with a resolution of $1000$. The mean persistence landscapes were computed on truncated persistence diagrams, with a confidence of $\alpha = 0.95$ for a representative of a persistent homology class tracked on the filtration.}
\label{homgroups}
\end{figure}

>>>>

\begin{table*}[t!]
\centering
\caption{Counts of the representatives per homology group from $\text{PL}(X)$.}
\label{figure3}
\begin{tabular}{@{}rcccccccccccccc@{}}
\toprule \multirow{2}{*}{\backslashbox{\texttt{Data} \strut}{\strut \texttt{Features}}} & \phantom{abc} & \multicolumn{5}{c}{\texttt{Homology groups}} &&& \multicolumn{6}{c}{\texttt{$\approx$ embedding dimension}}\\
\cmidrule{3-7} \cmidrule{10-15} & & $H_0$ & $H_1$ & $H_2$ & $H_3$ & $H_4$ &&& $p$ & $q \vert {H_1}$ & $q \vert {H_2}$ & $q \vert {H_3}$ & $q \vert {H_4}$ & $\dim U$\\
\midrule
\texttt{cifar10} && 12 & 16 & 40 & 59 & 50 &&& $12$ & $16$ & $9 \scriptstyle{\pm 4}$ & $8 \scriptstyle{\pm 3}$ & $7 \scriptstyle{\pm 15}$ & $92 \scriptstyle{\pm 44}$\\
\texttt{cifar100} && 13 & 18 & 34 & 46 & 48 &&& $13$ & $18$ & $9 \scriptstyle{\pm 2}$ & $8 \scriptstyle{\pm 10}$ & $7 \scriptstyle{\pm 13}$ & $97 \scriptstyle{\pm 50}$\\
\midrule
\end{tabular}
\label{stats}
\end{table*}
